### 2015-04-15 Dissertation/chapter-comparison_algorithms.tex
Broken reference

This goal is formalized using model scoring from Bayesian statistics. In its raw form this
almost always creates near infinitesimal results, calculating fractions which include factorials of $\mu$
and products over $N$. However, through algebraic manipulation discussed in Appendix~\ref{sec-appendix}, we
derived a simplified form shown in Equation~\ref{eq-hboa-final}.
Here $l$ is a leaf in tree $i$, with $l'$ and $l''$ the results of splitting $l$. $m_i(l)$ is the number
of solutions which reach $l$ and $m_i(x_i, l)$ is the number of solutions which reach $l$ with the given value
for $x_i$.
If no proposed split satisfies the inequality, iteration stops.
If multiple splits do, whichever maximizes the right side is chosen.

>>>>

This goal is formalized using model scoring from Bayesian statistics. In its raw form this
almost always creates near infinitesimal results, calculating fractions which include factorials of $\mu$
and products over $N$. However, through algebraic manipulation discussed in Appendix~\ref{chap-appendix-hboa}, we
derived a simplified form shown in Equation~\ref{eq-hboa-final}.
Here $l$ is a leaf in tree $i$, with $l'$ and $l''$ the results of splitting $l$. $m_i(l)$ is the number
of solutions which reach $l$ and $m_i(x_i, l)$ is the number of solutions which reach $l$ with the given value
for $x_i$.
If no proposed split satisfies the inequality, iteration stops.
If multiple splits do, whichever maximizes the right side is chosen.
